\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-10-09 submission/manuscript.Rmd

<!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->

Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real. Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits were associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness. This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].

In contrast, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with the confidence in real judgements [@chen2016intolerance; @jensen2014intolerance]. This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance]. **WHY IS THIS CONTRADICTORY? the next part seems to be about emotion regulation. While interesting, it's a bit of a non-sequitur no? And the previous explanation could almost be enough.** While the findings seem contradictory, they could possibly be interpreted through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive]. In fact, previous studies report that individuals with greater paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people]. This is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2019phenomenal]. As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that attenuated their confidence in real judgements. Future studies should clarify the role of emotions, particularly those related to anxiety, and attempt at delineating processes related to emotion perception and reaction from emotion regulation.

@@

<!-- Conclusion -->

In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities. The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions. We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship. We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake. Limitations include [**TO ADD**].

>>>>

<!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real. Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness. This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].

In contrast, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with the confidence in real judgements [@chen2016intolerance; @jensen2014intolerance]. This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance]. Interestingly, no significant effect on individuals' perceptions of realness was observed despite the shared positive links between uncertainty intolerance and paranoia [@zheng2022worry]. This suggests that being predisposed to view ambiguous scenarios negatively and having an enhanced sensitivity to social threats only partially explains the influence of paranoid traits on people's beliefs of realness. Given the lack of clear dissociation between the domains and mechanisms of paranoia and uncertainty intolerance [@king2017paranoia; @zheng2022worry], future studies should clarify the role of paranoid thinking on simulation monitoring processes, and attempt to delineate the specific emotional mechanisms involved.

@@

<!-- Conclusion -->
In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities. The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions. We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship. We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake. A limitation of the current paradigm includes requiring participants to judge the realness of faces they had prior exposure to, when they rated the face images on characteristics such as attractiveness. Hence, despite only a low number of faces being rated as highly familiar, subconscious recall of the face stimuli during re-exposure could have confounded perceptions of its realness. As such, future studies could modulate the extent to which facial memory affects realness judgements by incorporating novel face images during the re-exposure trial and examining if any significant difference is observed between the new and old images presented.
